The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Fix missing backslash before "python"

A prototype for the low-level analysis is \texttt{ctapipe} \citep{ctapipe},
a python package developed to perform all the necessary tasks to perform data processing, from the raw data
of Cherenkov telescopes to the reconstructed event lists.
The high-level analysis (or CTA science tools) will be based on the Astropy affiliated package
Gammapy~\citep{gammapy}.
Both Gammapy and \texttt{ctapipe} make heavy use of the \astropy core package, mainly for units, times, coordinate transformations,
tables, and FITS I/O.
As CTA will record gamma-ray events with a rate of up to $10\,000$ events per second,
it needs to perform a large number of coordinate transformations.
To enable this, CTA member M.~Nöthe contributed a major performance improvement
for large numbers of coordinates with different observation times,
based on earlier work by B.~Winkel.
Together with Gammapy maintainer A.~Donath and former maintainer C.~Deil,
a total of 107 merged pull requests were contributed to astropy.

>>>>

A prototype for the low-level analysis is \texttt{ctapipe} \citep{ctapipe},
a \python package developed to perform all the necessary tasks to perform data processing, from the raw data
of Cherenkov telescopes to the reconstructed event lists.
The high-level analysis (or CTA science tools) will be based on the Astropy affiliated package
Gammapy~\citep{gammapy}.
Both Gammapy and \texttt{ctapipe} make heavy use of the \astropy core package, mainly for units, times, coordinate transformations,
tables, and FITS I/O.
As CTA will record gamma-ray events with a rate of up to $10\,000$ events per second,
it needs to perform a large number of coordinate transformations.
To enable this, CTA member M.~Nöthe contributed a major performance improvement
for large numbers of coordinates with different observation times,
based on earlier work by B.~Winkel.
Together with Gammapy maintainer A.~Donath and former maintainer C.~Deil,
a total of 107 merged pull requests were contributed to astropy.
